---
title: "Additional analyses"
output:
  html_document:
    toc: TRUE
    toc_float:
      collapsed: FALSE
    toc_depth: 2
    code_folding: hide
    df_print: paged
bibliography      : 
  - "bibliography/r-references.bib"
  - "bibliography/references.bib"
  # pdf_document:
  #   toc: TRUE
---

```{r knitr-setup, include=F}
set.seed(170819)
knitr::opts_chunk$set(warning=F, echo=T, error=F, message=F, cache=T, max.row=20)
options(digits=2, width=260, scipen=999)
```

 - Here you can find the code and the results of all additional analyses. 
 - To see a good overview of the results, I recommend you directly go down to the Figures section. 
 - But if you're interested in how the analyses were executed, just tag along.
 - To see the code, click on button "Code". Alternatively, you can download the rmd file from the github repo.
 - To execute the code, first download the actual data from AUSSDA (https://doi.org/10.11587/28KQNS), save as .csv, then run analysis.rmd, then this file
 - Note that this paper uses an advance version consisting of 32 waves, which is at the time of writing not officially published.

# Set-up

Load packages.

```{r r-setup, results='hide'}
# install packages
# devtools::install_github("https://github.com/tdienlin/td@v.0.0.2.5")

# define packages
packages <- c("broom.mixed", "brms", "devtools", "GGally", "ggplot2", 
              "gridExtra", "kableExtra", "knitr", "lavaan", "lme4", 
              "magrittr", "mice", "mvnormalTest", 
              "PerFit", "psych", "quanteda.textstats", "semTools", "tidyverse")

# load packages
lapply(c(packages, "td"), library, character.only = TRUE)

# load workspace
load("data/workspace_1.RData")
```

# With additional covariates

These models include additional covariates that weren't preregistered. These are:

- Trust in ORF
- Trust in police
- Trust in parliament
- Trust in health sector
- Trust in government
- Trust in army

## Life satisfaction

```{r}
model_life_sat_lmer_add <- with(d_long_mim_mice, exp =  
                                lmerTest::lmer(life_sat ~
                                        (1 | id) + (1 | wave) + 
                                        soc_med_read_w + soc_med_like_share_w + soc_med_post_w  + 
                                        soc_med_fb_w + soc_med_ig_w + soc_med_wa_w + soc_med_yt_w + soc_med_tw_w +
                                        soc_med_read_b + soc_med_like_share_b + soc_med_post_b + 
                                        soc_med_fb_b + soc_med_ig_b + soc_med_wa_b + soc_med_yt_b + soc_med_tw_b +  
                                        age + male + born_aus + born_aus_prnts + edu_fac + employment_fac +
                                        res_vienna + acc_bal + acc_gar + home_sqm + corona_pos +
                                        hh_income_b +
                                        hh_adults +
                                        hh_child18 + hh_child17 + hh_child14 + hh_child5 + hh_child2 + hh_oldfam + hh_outfam + hh_partner +
                                        home_owner +
                                        med_txt_kro_b + med_txt_sta_b + med_txt_pre_b + med_txt_oes_b + med_txt_kur_b + med_txt_slz_b + med_txt_son_b + 
                                        med_vid_orf_b + med_vid_pri_b + 
                                        risk_prop_b + loc_cntrl_int_m_b + 
                                        act_wrk_w + act_spo_w + act_frn_w + act_sho_w + act_pet_w + 
                                        act_wrk_b + act_spo_b + act_frn_b + act_sho_b + act_pet_b +
                                        sat_dem_w + sat_dem_b + 
                                        health_w + health_b +
                                        trst_media_w + trst_police_w + trst_media_w + trst_hlthsec_w + trst_gov_w + trst_army_w +
                                        trst_media_b + trst_police_b + trst_media_b + trst_hlthsec_b + trst_gov_b + trst_army_b
                                      ))
model_life_sat_lmer_add <- summary(pool(model_life_sat_lmer_add), conf.int = TRUE)
model_life_sat_lmer_add %>% 
  as.data.frame %>% 
  select(term, estimate, `2.5 %`, `97.5 %`, p.value) %>% 
  mutate(p.value = td::my_round(p.value, "p"))
```

## Positive Affect

```{r}
model_aff_pos_lmer_add <- with(d_long_mim_mice, exp =  
                           lmerTest::lmer(aff_pos_m ~ 
                                        (1 | id) + (1 | wave) + 
                                        soc_med_read_w + soc_med_like_share_w + soc_med_post_w  + 
                                        soc_med_fb_w + soc_med_ig_w + soc_med_wa_w + soc_med_yt_w + soc_med_tw_w +
                                        soc_med_read_b + soc_med_like_share_b + soc_med_post_b + 
                                        soc_med_fb_b + soc_med_ig_b + soc_med_wa_b + soc_med_yt_b + soc_med_tw_b +  
                                        age + male + born_aus + born_aus_prnts + edu_fac + employment_fac +
                                        res_vienna + acc_bal + acc_gar + home_sqm + corona_pos +
                                        hh_income_b +
                                        hh_adults +
                                        hh_child18 + hh_child17 + hh_child14 + hh_child5 + hh_child2 + hh_oldfam + hh_outfam + hh_partner +
                                        home_owner +
                                        med_txt_kro_b + med_txt_sta_b + med_txt_pre_b + med_txt_oes_b + med_txt_kur_b + med_txt_slz_b + med_txt_son_b + 
                                        med_vid_orf_b + med_vid_pri_b + 
                                        risk_prop_b + loc_cntrl_int_m_b + 
                                        act_wrk_w + act_spo_w + act_frn_w + act_sho_w + act_pet_w + 
                                        act_wrk_b + act_spo_b + act_frn_b + act_sho_b + act_pet_b +
                                        sat_dem_w + sat_dem_b + 
                                        health_w + health_b +
                                        trst_media_w + trst_police_w + trst_media_w + trst_hlthsec_w + trst_gov_w + trst_army_w +
                                        trst_media_b + trst_police_b + trst_media_b + trst_hlthsec_b + trst_gov_b + trst_army_b
                                        ))
model_aff_pos_lmer_add <- summary(pool(model_aff_pos_lmer_add), conf.int = TRUE)
model_aff_pos_lmer_add %>% 
  as.data.frame %>% 
  select(term, estimate, `2.5 %`, `97.5 %`, p.value) %>% 
  mutate(p.value = td::my_round(p.value, "p"))
```

## Negative Affect

```{r}
model_aff_neg_lmer_add <- with(d_long_mim_mice, exp =  
                               lmerTest::lmer(aff_neg_m ~ 
                                        (1 | id) + (1 | wave) + 
                                        soc_med_read_w + soc_med_like_share_w + soc_med_post_w  + 
                                        soc_med_fb_w + soc_med_ig_w + soc_med_wa_w + soc_med_yt_w + soc_med_tw_w +
                                        soc_med_read_b + soc_med_like_share_b + soc_med_post_b + 
                                        soc_med_fb_b + soc_med_ig_b + soc_med_wa_b + soc_med_yt_b + soc_med_tw_b +  
                                        age + male + born_aus + born_aus_prnts + edu_fac + employment_fac +
                                        res_vienna + acc_bal + acc_gar + home_sqm + corona_pos +
                                        hh_income_b +
                                        hh_adults +
                                        hh_child18 + hh_child17 + hh_child14 + hh_child5 + hh_child2 + hh_oldfam + hh_outfam + hh_partner +
                                        home_owner +
                                        med_txt_kro_b + med_txt_sta_b + med_txt_pre_b + med_txt_oes_b + med_txt_kur_b + med_txt_slz_b + med_txt_son_b + 
                                        med_vid_orf_b + med_vid_pri_b + 
                                        risk_prop_b + loc_cntrl_int_m_b + 
                                        act_wrk_w + act_spo_w + act_frn_w + act_sho_w + act_pet_w + 
                                        act_wrk_b + act_spo_b + act_frn_b + act_sho_b + act_pet_b +
                                        sat_dem_w + sat_dem_b + 
                                        health_w + health_b +
                                        trst_media_w + trst_police_w + trst_media_w + trst_hlthsec_w + trst_gov_w + trst_army_w +
                                        trst_media_b + trst_police_b + trst_media_b + trst_hlthsec_b + trst_gov_b + trst_army_b
                                        ))
model_aff_neg_lmer_add <- summary(pool(model_aff_neg_lmer_add), conf.int = TRUE)
model_aff_neg_lmer_add %>% 
  as.data.frame %>% 
  select(term, estimate, `2.5 %`, `97.5 %`, p.value) %>% 
  mutate(p.value = td::my_round(p.value, "p"))
```

# Preregistered

Several changes were introduced during peer review (multiple imputation, imputation of all participants, inclusion of all variables). In what follows, please find the results as originally planned (but with some necessary deviations; for example not preregistered all variables could be included).

 - Use data-set in which participants with >50% data were removed. 
 - Also use factor scores (possible without multiple imputation).
 
 Because no multiple imputation was used, output looks differently.

## Life satisfaction

```{r}
model_life_sat_lmer_pre <- lmerTest::lmer(life_sat ~
                                        (1 | id) + (1 | wave) + 
                                        soc_med_read_w + soc_med_like_share_w + soc_med_post_w  + 
                                        soc_med_fb_w + soc_med_ig_w + soc_med_wa_w + soc_med_yt_w + soc_med_tw_w +
                                        soc_med_read_b + soc_med_like_share_b + soc_med_post_b + 
                                        soc_med_fb_b + soc_med_ig_b + soc_med_wa_b + soc_med_yt_b + soc_med_tw_b +  
                                        age + male + born_aus + born_aus_prnts + edu_fac + employment_fac +
                                        res_vienna + acc_bal + acc_gar + home_sqm + corona_pos +
                                        med_txt_kro_b + med_txt_sta_b + med_txt_pre_b + med_txt_oes_b + med_txt_kur_b + med_txt_slz_b + med_txt_son_b + 
                                        med_vid_orf_b + med_vid_pri_b + 
                                        risk_prop_b + loc_cntrl_int_m_b + 
                                        act_wrk_w + act_spo_w + act_frn_w + act_sho_w + act_pet_w + 
                                        act_wrk_b + act_spo_b + act_frn_b + act_sho_b + act_pet_b +
                                        sat_dem_w + sat_dem_b + 
                                        health_w + health_b 
                                      , data = d_long_50_imp)
summary(model_life_sat_lmer_pre)
```

## Positive Affect

```{r}
model_aff_pos_lmer_pre <- lmerTest::lmer(aff_pos_fs ~ 
                                        (1 | id) + (1 | wave) + 
                                        soc_med_read_w + soc_med_like_share_w + soc_med_post_w  + 
                                        soc_med_fb_w + soc_med_ig_w + soc_med_wa_w + soc_med_yt_w + soc_med_tw_w +
                                        soc_med_read_b + soc_med_like_share_b + soc_med_post_b + 
                                        soc_med_fb_b + soc_med_ig_b + soc_med_wa_b + soc_med_yt_b + soc_med_tw_b +  
                                        age + male + born_aus + born_aus_prnts + edu_fac + employment_fac +
                                        res_vienna + acc_bal + acc_gar + home_sqm + corona_pos +
                                        med_txt_kro_b + med_txt_sta_b + med_txt_pre_b + med_txt_oes_b + med_txt_kur_b + med_txt_slz_b + med_txt_son_b + 
                                        med_vid_orf_b + med_vid_pri_b + 
                                        risk_prop_b + loc_cntrl_int_m_b + 
                                        act_wrk_w + act_spo_w + act_frn_w + act_sho_w + act_pet_w + 
                                        act_wrk_b + act_spo_b + act_frn_b + act_sho_b + act_pet_b +
                                        sat_dem_w + sat_dem_b + 
                                        health_w + health_b 
                                      , data = d_long_50_imp)
summary(model_aff_pos_lmer_pre)
```

## Negative Affect

```{r}
model_aff_neg_lmer_pre <- lmerTest::lmer(aff_neg_fs ~ 
                                        (1 | id) + (1 | wave) + 
                                        soc_med_read_w + soc_med_like_share_w + soc_med_post_w  + 
                                        soc_med_fb_w + soc_med_ig_w + soc_med_wa_w + soc_med_yt_w + soc_med_tw_w +
                                        soc_med_read_b + soc_med_like_share_b + soc_med_post_b + 
                                        soc_med_fb_b + soc_med_ig_b + soc_med_wa_b + soc_med_yt_b + soc_med_tw_b +  
                                        age + male + born_aus + born_aus_prnts + edu_fac + employment_fac +
                                        res_vienna + acc_bal + acc_gar + home_sqm + corona_pos +
                                        med_txt_kro_b + med_txt_sta_b + med_txt_pre_b + med_txt_oes_b + med_txt_kur_b + med_txt_slz_b + med_txt_son_b + 
                                        med_vid_orf_b + med_vid_pri_b + 
                                        risk_prop_b + loc_cntrl_int_m_b + 
                                        act_wrk_w + act_spo_w + act_frn_w + act_sho_w + act_pet_w + 
                                        act_wrk_b + act_spo_b + act_frn_b + act_sho_b + act_pet_b +
                                        sat_dem_w + sat_dem_b + 
                                        health_w + health_b
                                      , data = d_long_50_imp)
summary(model_aff_neg_lmer_pre)
```

# Preregistered without imputation

Same as before, but now don't use any imputed data whatsoever. Was preregistered as additional analysis to provide comparison.

We first need to export factor scores for variables without imputed data. Note that I don't report results of mean scores to save space, as results would be highly similar.

```{r}
model <- "
aff_pos =~ a1*aff_pos_1 + a2*aff_pos_2 + a3*aff_pos_3
"
cfa_aff_pos <- cfa(model, d_long_50, group = "wave", estimator = "MLM")
d_long_50$aff_pos_fs <- get_fs(cfa_aff_pos)

model <- "
aff_neg =~ a1*aff_neg_1 + a2*aff_neg_2 + a3*aff_neg_3 + a4*aff_neg_4 + a5*aff_neg_5 + a6*aff_neg_6
"
cfa_aff_neg <- cfa(model, d_long_50, group = "wave", estimator = "MLM")
d_long_50$aff_neg_fs <- get_fs(cfa_aff_neg)
```

## Life satisfaction

```{r}
model_life_sat_lmer_noi <- lmerTest::lmer(life_sat ~
                                        (1 | id) + (1 | wave) + 
                                        soc_med_read_w + soc_med_like_share_w + soc_med_post_w  + 
                                        soc_med_fb_w + soc_med_ig_w + soc_med_wa_w + soc_med_yt_w + soc_med_tw_w +
                                        soc_med_read_b + soc_med_like_share_b + soc_med_post_b + 
                                        soc_med_fb_b + soc_med_ig_b + soc_med_wa_b + soc_med_yt_b + soc_med_tw_b +  
                                        age + male + born_aus + born_aus_prnts + edu_fac + employment_fac +
                                        res_vienna + acc_bal + acc_gar + home_sqm + corona_pos +
                                        med_txt_kro_b + med_txt_sta_b + med_txt_pre_b + med_txt_oes_b + med_txt_kur_b + med_txt_slz_b + med_txt_son_b + 
                                        med_vid_orf_b + med_vid_pri_b + 
                                        risk_prop_b + loc_cntrl_int_m_b + 
                                        act_wrk_w + act_spo_w + act_frn_w + act_sho_w + act_pet_w + 
                                        act_wrk_b + act_spo_b + act_frn_b + act_sho_b + act_pet_b +
                                        sat_dem_w + sat_dem_b + 
                                        health_w + health_b 
                                      , data = d_long_50)
summary(model_life_sat_lmer_noi)
```

## Positive Affect

```{r}
model_aff_pos_lmer_noi <- lmerTest::lmer(aff_pos_fs ~ 
                                        (1 | id) + (1 | wave) + 
                                        soc_med_read_w + soc_med_like_share_w + soc_med_post_w  + 
                                        soc_med_fb_w + soc_med_ig_w + soc_med_wa_w + soc_med_yt_w + soc_med_tw_w +
                                        soc_med_read_b + soc_med_like_share_b + soc_med_post_b + 
                                        soc_med_fb_b + soc_med_ig_b + soc_med_wa_b + soc_med_yt_b + soc_med_tw_b +  
                                        age + male + born_aus + born_aus_prnts + edu_fac + employment_fac +
                                        res_vienna + acc_bal + acc_gar + home_sqm + corona_pos +
                                        med_txt_kro_b + med_txt_sta_b + med_txt_pre_b + med_txt_oes_b + med_txt_kur_b + med_txt_slz_b + med_txt_son_b + 
                                        med_vid_orf_b + med_vid_pri_b + 
                                        risk_prop_b + loc_cntrl_int_m_b + 
                                        act_wrk_w + act_spo_w + act_frn_w + act_sho_w + act_pet_w + 
                                        act_wrk_b + act_spo_b + act_frn_b + act_sho_b + act_pet_b +
                                        sat_dem_w + sat_dem_b + 
                                        health_w + health_b 
                                      , data = d_long_50)
summary(model_aff_pos_lmer_noi)
```

## Negative Affect

```{r}
model_aff_neg_lmer_noi <- lmerTest::lmer(aff_neg_fs ~ 
                                        (1 | id) + (1 | wave) + 
                                        soc_med_read_w + soc_med_like_share_w + soc_med_post_w  + 
                                        soc_med_fb_w + soc_med_ig_w + soc_med_wa_w + soc_med_yt_w + soc_med_tw_w +
                                        soc_med_read_b + soc_med_like_share_b + soc_med_post_b + 
                                        soc_med_fb_b + soc_med_ig_b + soc_med_wa_b + soc_med_yt_b + soc_med_tw_b +  
                                        age + male + born_aus + born_aus_prnts + edu_fac + employment_fac +
                                        res_vienna + acc_bal + acc_gar + home_sqm + corona_pos +
                                        med_txt_kro_b + med_txt_sta_b + med_txt_pre_b + med_txt_oes_b + med_txt_kur_b + med_txt_slz_b + med_txt_son_b + 
                                        med_vid_orf_b + med_vid_pri_b + 
                                        risk_prop_b + loc_cntrl_int_m_b + 
                                        act_wrk_w + act_spo_w + act_frn_w + act_sho_w + act_pet_w + 
                                        act_wrk_b + act_spo_b + act_frn_b + act_sho_b + act_pet_b +
                                        sat_dem_w + sat_dem_b + 
                                        health_w + health_b
                                      , data = d_long_50)
summary(model_aff_neg_lmer_noi)
```

# Figures

 - In what follows, see figure with all results combined. 
 - Results show that different models are very comparable. 
 - The model without control variables stands a bit out, showing that controlling for additional varying variables is important.
 - The preregistered model without imputation also has larger confidence intervals, which was to be expected given fewer data.

## Within

```{r warning=F, fig.height=5}
# get data
dat_fig_results_activity_pub <- get_dat_res(
  model_aff_neg_lmer_pub, model_aff_pos_lmer_pub, model_life_sat_lmer_pub, 
  type = "activity", analysis = "1. preregistered")

dat_fig_results_channel_pub <- get_dat_res(
  model_aff_neg_lmer_pub, model_aff_pos_lmer_pub, model_life_sat_lmer_pub, 
  type = "channels", analysis = "1. preregistered")

dat_fig_results_within_pub <- rbind(
  cbind(dat_fig_results_activity_pub, comm = "activity"), 
  cbind(dat_fig_results_channel_pub, comm = "channel")) %>% 
  filter(type == "within")

dat_fig_results_activity_nco <- get_dat_res(
  model_aff_neg_lmer_nco, model_aff_pos_lmer_nco, model_life_sat_lmer_nco, 
  type = "activity", analysis = "2. no covars")

dat_fig_results_channel_nco <- get_dat_res(
  model_aff_neg_lmer_nco, model_aff_pos_lmer_nco, model_life_sat_lmer_nco, 
  type = "channels", analysis = "2. no covars")

dat_fig_results_within_nco <- rbind(
  cbind(dat_fig_results_activity_nco, comm = "activity"), 
  cbind(dat_fig_results_channel_nco, comm = "channel")) %>% 
  filter(type == "within")

dat_fig_results_activity_add <- get_dat_res(
  model_aff_neg_lmer_add, model_aff_pos_lmer_add, model_life_sat_lmer_add, 
  type = "activity", analysis = "3. additional covars")

dat_fig_results_channel_add <- get_dat_res(
  model_aff_neg_lmer_add, model_aff_pos_lmer_add, model_life_sat_lmer_add, 
  type = "channels", analysis = "3. additional covars")

dat_fig_results_within_add <- rbind(
  cbind(dat_fig_results_activity_add, comm = "activity"), 
  cbind(dat_fig_results_channel_add, comm = "channel")) %>% 
  filter(type == "within")

dat_fig_results_activity_pre <- get_dat_res(
  model_aff_neg_lmer_pre, model_aff_pos_lmer_pre, model_life_sat_lmer_pre, 
  type = "activity", analysis = "4. preregistered")

dat_fig_results_channel_pre <- get_dat_res(
  model_aff_neg_lmer_pre, model_aff_pos_lmer_pre, model_life_sat_lmer_pre, 
  type = "channels", analysis = "4. preregistered")

dat_fig_results_within_pre <- rbind(
  cbind(dat_fig_results_activity_pre, comm = "activity"), 
  cbind(dat_fig_results_channel_pre, comm = "channel")) %>% 
  filter(type == "within")

dat_fig_results_activity_noi <- get_dat_res(
  model_aff_neg_lmer_noi, model_aff_pos_lmer_noi, model_life_sat_lmer_noi, 
  type = "activity", analysis = "5. prereg no imp")

dat_fig_results_channel_noi <- get_dat_res(
  model_aff_neg_lmer_noi, model_aff_pos_lmer_noi, model_life_sat_lmer_noi, 
  type = "channels", analysis = "5. prereg no imp")

dat_fig_results_within_noi <- rbind(
  cbind(dat_fig_results_activity_noi, comm = "activity"), 
  cbind(dat_fig_results_channel_noi, comm = "channel")) %>% 
  filter(type == "within")

dat_fig_results_within_comp <- rbind(
  dat_fig_results_within_pub,
  dat_fig_results_within_nco,
  dat_fig_results_within_add,
  dat_fig_results_within_pre,
  dat_fig_results_within_noi
)
# make figure
fig_results_within_comp <- make_graph_res(
  dat_fig_results_within_comp,
  sesoi = "est",
  facet = "comm"
  )
fig_results_within_comp

# safe figure
ggsave("figures/fig_results_within_comparison.pdf", 
       width = 7, height = 5,
       plot = fig_results_within_comp)
```

## Between

```{r warning=FALSE, fig.height=5}
# get data
dat_fig_results_activity_pub <- get_dat_res(
  model_aff_neg_lmer_pub, model_aff_pos_lmer_pub, model_life_sat_lmer_pub, 
  type = "activity", analysis = "1. preregistered")

dat_fig_results_channel_pub <- get_dat_res(
  model_aff_neg_lmer_pub, model_aff_pos_lmer_pub, model_life_sat_lmer_pub, 
  type = "channels", analysis = "1. preregistered")

dat_fig_results_between_pub <- rbind(
  cbind(dat_fig_results_activity_pub, comm = "activity"), 
  cbind(dat_fig_results_channel_pub, comm = "channel")) %>% 
  filter(type == "between")

dat_fig_results_activity_nco <- get_dat_res(
  model_aff_neg_lmer_nco, model_aff_pos_lmer_nco, model_life_sat_lmer_nco, 
  type = "activity", analysis = "2. no covars")

dat_fig_results_channel_nco <- get_dat_res(
  model_aff_neg_lmer_nco, model_aff_pos_lmer_nco, model_life_sat_lmer_nco, 
  type = "channels", analysis = "2. no covars")

dat_fig_results_between_nco <- rbind(
  cbind(dat_fig_results_activity_nco, comm = "activity"), 
  cbind(dat_fig_results_channel_nco, comm = "channel")) %>% 
  filter(type == "between")

dat_fig_results_activity_add <- get_dat_res(
  model_aff_neg_lmer_add, model_aff_pos_lmer_add, model_life_sat_lmer_add, 
  type = "activity", analysis = "3. additional covars")

dat_fig_results_channel_add <- get_dat_res(
  model_aff_neg_lmer_add, model_aff_pos_lmer_add, model_life_sat_lmer_add, 
  type = "channels", analysis = "3. additional covars")

dat_fig_results_between_add <- rbind(
  cbind(dat_fig_results_activity_add, comm = "activity"), 
  cbind(dat_fig_results_channel_add, comm = "channel")) %>% 
  filter(type == "between")

dat_fig_results_activity_pre <- get_dat_res(
  model_aff_neg_lmer_pre, model_aff_pos_lmer_pre, model_life_sat_lmer_pre, 
  type = "activity", analysis = "4. preregistered")

dat_fig_results_channel_pre <- get_dat_res(
  model_aff_neg_lmer_pre, model_aff_pos_lmer_pre, model_life_sat_lmer_pre, 
  type = "channels", analysis = "4. preregistered")

dat_fig_results_between_pre <- rbind(
  cbind(dat_fig_results_activity_pre, comm = "activity"), 
  cbind(dat_fig_results_channel_pre, comm = "channel")) %>% 
  filter(type == "between")

dat_fig_results_activity_noi <- get_dat_res(
  model_aff_neg_lmer_noi, model_aff_pos_lmer_noi, model_life_sat_lmer_noi, 
  type = "activity", analysis = "5. prereg no imp")

dat_fig_results_channel_noi <- get_dat_res(
  model_aff_neg_lmer_noi, model_aff_pos_lmer_noi, model_life_sat_lmer_noi, 
  type = "channels", analysis = "5. prereg no imp")

dat_fig_results_between_noi <- rbind(
  cbind(dat_fig_results_activity_noi, comm = "activity"), 
  cbind(dat_fig_results_channel_noi, comm = "channel")) %>% 
  filter(type == "between")

dat_fig_results_between_comp <- rbind(
  dat_fig_results_between_pub,
  dat_fig_results_between_nco,
  dat_fig_results_between_add,
  dat_fig_results_between_pre,
  dat_fig_results_between_noi
)
# make figure
fig_results_between_comp <- make_graph_res(
  dat_fig_results_between_comp,
  sesoi = "est",
  facet = "comm"
  )
fig_results_between_comp

# safe figure
ggsave("figures/fig_results_between_comparison.pdf", 
       width = 7, height = 5,
       plot = fig_results_between_comp)
```

```{r eval=F}
save.image("data/workspace_2.RData")
```
