---
title: "Analyses"
output:
  html_document:
    toc: TRUE
    toc_float:
      collapsed: FALSE
    toc_depth: 2
    code_folding: hide
    df_print: paged
bibliography      : 
  - "bibliography/r-references.bib"
  - "bibliography/references.bib"
  # pdf_document:
  #   toc: TRUE
---

```{r knitr-setup, include=F}
set.seed(170819)
knitr::opts_chunk$set(warning=F, echo=T, error=F, message=F, cache=T, rows.print=20)
options(digits=2, width=260, scipen=999)
```

 - Here you can find the code and the results of all analyses. 
 - To see the code, click on button "Code". A
 - Alternatively, you can download the rmd file from the github repo.
 - The data are hosted on aussda. Please download them separately, to rerun the analyses (https://doi.org/10.11587/28KQNS). 
 - Note that this paper uses an advance version consisting of 32 waves, which is at the time of writing not officially published.

# Set-up

Load packages.

```{r r-setup, results='hide', cache=F}
# install packages
# devtools::install_github("https://github.com/tdienlin/td@v.0.0.2.5")

# define packages
packages <- c("broom.mixed", "brms", "devtools", "GGally", "ggplot2", 
              "gridExtra", "kableExtra", "knitr", "lavaan", "lme4", 
              "magrittr", "mice", #"mvnormalTest", 
              "PerFit", "psych", "quanteda.textstats", "semTools", "tidyverse")

# load packages
lapply(c(packages, "td"), library, character.only = TRUE)
```

## Session info

Provide session info to make results reproducible.

```{r}
sessionInfo()
```

## Custom functions

### find_var

Find variables in dataset.

```{r}
find_var <- function(name, data = doc)(
  # finds the variables names for an item for each wave
    data %>%
    filter(Label == name) %>%
    select(Variable) %>%
    unlist() %>%
    set_names(sub("\\_.*", "", .))
)
# find_var <- function(name, data = doc)(
#   # finds the variables names for an item for each wave
#     data %>% 
#     filter(`Variable names (DE)` == name) %>% 
#     select(`VARNAME (CA)`) %>% 
#     unlist() %>% 
#     set_names(sub("\\_.*", "", .))
# )
```

### get_specs

Extract characteristics from fitted lmer models.

```{r}
get_specs <- function(model){
    # Get mean, max, and min values

    dat <- coefficients(model)$wave
    specs <- data.frame(
    sd = attr(VarCorr(model), "sc"),
    min = min(dat),
    max = max(dat),
    mean = mean(dat$`(Intercept)`)
  )
}
```

### get_dat

Get data from fitted lmer objects for descriptives.

```{r}
get_dat <- function(model){
  coefficients(model)$wave %>% 
  tibble::rownames_to_column("wave") %>% 
  rename(value = "(Intercept)") %>% 
  mutate(wave = as.integer(.$wave),
         value = as.numeric(.$value)) 
} 
```

### get_rel

Determine average reliability for measures across waves

```{r}
get_rel <- function(data, waves=24){
  
  # extract average reliability from lavaan fitted cfa with several groups
  reliability(data) %>% 
  unlist() %>% 
  matrix(5, waves) %>% 
  as.data.frame() %>% 
  set_rownames(c("alpha", "omega", "omega2", "omega3", "avevar")) %>% 
  summarise(omega = rowMeans(.["omega",])) %>% 
  return()
}
```

### make_graph

Make graph of variables' development.

```{r}
make_graph <- function(model, title, ll, ul, line = FALSE, labels = FALSE, lmer=TRUE, legend=TRUE){

    if(isTRUE(lmer)){
      dat <- get_dat(model)
    } else{
    dat <- model
  }
    
  graph <- 
    ggplot(dat, aes(wave, value, color = dimension)) +
    {if(legend) theme(
      legend.position = c(0.85, 0.8),
      legend.title = element_blank()
      )} + 
    {if(!legend) theme(
      legend.position = "none"
    )} +
    theme(axis.title.x=element_blank()) +
    coord_cartesian(ylim = c(ll, ul)) +
    ggtitle(title) +
    {if(line) geom_smooth(se = FALSE, method = 'loess')} +
    # geom_point() +
    scale_color_manual(values=c("dodgerblue3", "deepskyblue2", "magenta2", "green2", "red"))
  graph
}
```

### get_dat_res

Get data of lmer objects for results.

```{r}
# get data
get_dat_res <- function(data_aff_neg, data_aff_pos, data_life_sat, type, analysis = NULL){
  
  if(isTRUE(class(data_aff_neg) == "lmerModLmerTest")) {
         dat_fig_results <- 
           broom.mixed::tidy(data_aff_neg, conf.int = T) %>% 
           mutate(dv = "aff_neg") %>% 
           rbind(
             broom.mixed::tidy(data_aff_pos, conf.int = T) %>% 
               mutate(dv = "aff_pos")) %>% 
           rbind(
             broom.mixed::tidy(data_life_sat, conf.int = T) %>% 
               mutate(dv = "life_sat"))
         } else{ 
           dat_fig_results <- 
             data_aff_neg %>% 
             mutate(dv = "aff_neg") %>% 
             rbind(data_aff_pos %>% 
                   mutate(dv = "aff_pos")) %>% 
             rbind(data_life_sat %>% 
                     mutate(dv = "life_sat")) %>% 
           rename(conf.low = `2.5 %`, conf.high = `97.5 %`)
           }
  dat_fig_results %<>% 
  mutate(
    type = ifelse(grepl(".*_w\\>", .$term), "within", "between"),
    iv = gsub("_(w|b)\\>", "", .$term)
         ) %>%
  mutate(
    type = factor(.$type, 
                  levels = c("within", "between")),
    dv = factor(.$dv, 
                levels = c("life_sat", "aff_pos", "aff_neg"),
                labels = c("Life satisfaction", "Positive affect", "Negative affect")),
    Analysis = analysis
  ) %>% 
  select(dv, iv, type, Analysis, estimate, conf.low, conf.high, p.value)

  # select Social Media type of activity
  if(type == "activity") {
    dat_fig_results %<>%
    filter(iv %in% c("soc_med_read", "soc_med_like_share", "soc_med_post")) %>% 
    mutate(
      iv = factor(.$iv, 
                  levels = c("soc_med_post", "soc_med_like_share", "soc_med_read"), 
                  labels = c("Posting", "Liking & Sharing", "Reading"))
    )
  } else if(type == "channels"){
    dat_fig_results %<>%
    filter(iv %in% c("soc_med_fb", "soc_med_ig", "soc_med_wa", "soc_med_yt", "soc_med_tw")) %>% 
    mutate(iv = factor(.$iv, levels = c("soc_med_yt", "soc_med_wa", "soc_med_ig", "soc_med_tw", "soc_med_fb"), labels = c("YouTube", "WhatsApp", "Instagram", "Twitter", "Facebook")))
  } else if(type == "control"){
    dat_fig_results %<>%
      filter(iv %in% c("male", "health", "loc_cntrl_int_m", #"employment_facPublic service", 
                       "act_spo", "sat_dem")) %>% 
      mutate(iv = factor(.$iv, levels = c("male", "health", "loc_cntrl_int_m", #"employment_facPublic service", 
                                          "act_spo", "sat_dem"), 
                         labels = c("Male", "Health", "Internal locus of control", #"Employed public service", 
                                    "Sport", "Satisfaction democracy")))
  }
  return(dat_fig_results)
}

```

### make_graph_res

Make graph of effects

```{r}
make_graph_res <- function(data, sesoi = NULL, legend = TRUE, facet = "comm", title = NULL){
  ggplot(data, aes(x = estimate, y = iv)) + 
  scale_color_manual(values = c("black", "grey75", "darkcyan", "deepskyblue", "cornflowerblue", "darkcyan", "aquamarine")) +
  geom_vline(xintercept = 0, lwd = .75, colour = "darkgrey") + 
  geom_errorbarh(aes(xmin = conf.low, xmax = conf.high, color = Analysis),
                lwd = .75, height = .2, position = position_dodge(-.7)) +
  geom_point(aes(color = Analysis), size = 1.5, position = position_dodge(-.7)) +
    {if(isTRUE(sesoi == "est")) geom_vline(data=filter(data, dv=="Life satisfaction"), aes(xintercept=-.3), colour="darkgrey", linetype = "dashed")} + 
    {if(isTRUE(sesoi == "est")) geom_vline(data=filter(data, dv=="Life satisfaction"), aes(xintercept=.3), colour="darkgrey", linetype = "dashed")} + 
    {if(isTRUE(sesoi == "est")) geom_vline(data=filter(data, dv!="Life satisfaction"), aes(xintercept=-.15), colour="darkgrey", linetype = "dashed")} +
    {if(isTRUE(sesoi == "est")) geom_vline(data=filter(data, dv!="Life satisfaction"), aes(xintercept=.15), colour="darkgrey", linetype = "dashed")} +
    {if(isTRUE(sesoi == "std")) geom_vline(aes(xintercept=.1), colour="darkgrey", linetype = "dashed")} + 
    {if(isTRUE(sesoi == "std")) geom_vline(aes(xintercept=-.1), colour="darkgrey", linetype = "dashed")} +   
  theme(
    axis.title.y = element_blank(),
    plot.title = element_text(hjust = .5),
    panel.spacing = unit(.9, "lines"),
    text = element_text(size = 12),
    axis.text.y = element_text(hjust = 1)
    ) +
  {if(!is.null(title)) ggtitle(title)} +
  {if(!isTRUE(legend)) theme(legend.position = "none")} + 
  # guides(colour = guide_legend(reverse=T)) +
    {if(facet == "comm")
      facet_grid(rows = vars(comm),
             cols = vars(dv),
             scales = "free",
             space = "free_y")
    } + 
    {if(facet == "analysis")
      facet_grid(rows = vars(type),
             cols = vars(dv),
             scales = "free",
             space = "free_y")
    }
}
```

### get_fs

Extract factor scores.

```{r}
get_fs <- function(model) {
  # the aim is to get factor scores on original scaling
  # hence export factor values for all items
  # then compute average
  dat_ov <- lavaan::lavPredict(model, type = "ov", assemble = TRUE) %>% 
    mutate(fs = rowMeans(.[1:3]))
  return(dat_ov$fs)
}
```

# Data Wrangling
## Load data

```{r}
# doc <- read_csv("documentation/10094_vi_de_v4_0.csv")
doc <- read_csv2("data/Variable_List_w1-34.csv")
# doc <- read_csv("documentation/W1-32_ACPP_Variablelist_V20220601.csv")
# d_raw <- read_csv("data/10094_da_de_v4_0.csv")
# d_raw_test <- read_csv("data/10094_da_de_v4_0.csv")
d_raw <- read_csv("data/W1-32_ACPP_V20220601.csv")
```

## Find names

Identify the names of each item for each wave.

```{r}
# identify variable names of items, using custom function
health <- find_var("Gesundheitszustand") # wsn't collected at wave 21
aff_neg_1 <- find_var("Depressivitaet: einsam")
aff_neg_2 <- find_var("Depressivitaet: aergerlich")
aff_neg_3 <- find_var("Depressivitaet: so niedergeschlagen")
aff_neg_4 <- find_var("Depressivitaet: sehr nervoes")
aff_neg_5 <- find_var("Depressivitaet: aengstlich")
aff_neg_6 <- find_var("Depressivitaet: bedrueckt und traurig")
aff_pos_1 <- find_var("Depressivitaet: ruhig und gelassen")
aff_pos_2 <- find_var("Depressivitaet: gluecklich")
aff_pos_3 <- find_var("Depressivitaet: voller Energie")
act_wrk <- find_var("Zuhause verlassen: Arbeit")
act_spo <- find_var("Zuhause verlassen: Sport")
act_frn <- find_var("Zuhause verlassen: Freunde oder Verwandte treffen")
act_sho <- find_var("Zuhause verlassen: Essen einkaufen")
act_pet <- find_var("Zuhause verlassen: Haustier ausfuehren")
sat_dem <- find_var("Demokratiezufriedenheit: Oesterreich")
work_h <- find_var("Arbeitsstunden: Jetzt pro Woche")
work_homeoff <- find_var("Aenderung berufliche Situation: Home-Office")
hh_income <- find_var("Aktuelles Haushaltseinkommen")
med_txt_kro <- find_var("Mediennutzung: Kronen Zeitung oder www.krone.at")
med_txt_sta <- find_var("Mediennutzung: Der Standard oder derstandard.at")
med_txt_pre <- find_var("Mediennutzung: Die Presse oder diepresse.com")
med_txt_oes <- find_var("Mediennutzung: Oesterreich oder oe24.at")
med_txt_kur <- find_var("Mediennutzung: Kurier oder kurier.at")
med_txt_slz <- find_var("Mediennutzung: Salzburger Nachrichten oder salzburg.at")
med_txt_son <- find_var("Mediennutzung: Sonstige oesterreichische Tageszeitungen")
med_vid_orf <- find_var("Mediennutzung: ORF (Nachrichten)")
med_vid_pri <- find_var("Mediennutzung: Privatfernsehen (Nachrichten)")
soc_med_fb <- find_var("Soziale Medien: Facebook")
soc_med_tw <- find_var("Soziale Medien: Twitter")
soc_med_ig <- find_var("Soziale Medien: Instagram")
soc_med_yt <- find_var("Soziale Medien: Youtube")
soc_med_wa <- find_var("Soziale Medien: WhatsApp")
soc_med_read <- find_var("Soziale Medien Aktivitaet: Postings zu Corona anderer lesen")
soc_med_like_share <- find_var("Soziale Medien Aktivitaet: Postings liken, teilen oder retweeten")
soc_med_post <- find_var("Soziale Medien Aktivitaet: selber Postings zu Corona verfassen")
life_sat <- find_var("Lebenszufriedenheit")
risk_prop <- find_var("Risikobereitschaft")
loc_cntrl_int_1 <- find_var("Psychologie: habe Leben selbst in der Hand")
loc_cntrl_int_2 <- find_var("Psychologie: Belohnung durch Anstrengung")
loc_cntrl_int_3 <- find_var("Psychologie: Fremdbestimmung")
loc_cntrl_int_4 <- find_var("Psychologie: Schicksal")
trst_media <- find_var("Vertrauen: ORF")
trst_police <- find_var("Vertrauen: Polizei")
trst_media <- find_var("Vertrauen: Parlament")
trst_hlthsec <- find_var("Vertrauen: Gesundheitswesen")
trst_gov <- find_var("Vertrauen: Bundesregierung")
trst_army <- find_var("Vertrauen: Bundesheer")
corona_pos <- c(
  find_var("Corona-Diagnose: Respondent"),
  find_var("Corona-Diagnose: Monat")
)
```

## Select variables

```{r}
d_wide <- d_raw %>% 
  select(
    id = RESPID,
    gender = SD_GENDER,
    acc_bal = SD_ACCESS_BALCONY,
    acc_gar = SD_ACCESS_GARDEN,
    year_birth = SD_BIRTHYEAR,
    born_aus = SD_BORN_AUSTRIA,
    born_aus_prnts = SD_MIGR_BACKGR,
    county = SD_BULA,
    edu = SD_EDU,
    employment = SD_EMPLSTATUS_FEB2020,
    hh_adults = SD_HH_ADULTS,
    hh_child18 = SD_HH_CHILD18,
    hh_child17 = SD_HH_TEENS,
    hh_child14 = SD_HH_CHILD14,
    hh_child5 = SD_HH_CHILD5,
    hh_child2 = SD_HH_CHILD2,
    hh_oldfam = SD_HH_OLDERFAM,
    hh_outfam = SD_HH_OUTERFAM,
    hh_partner = SD_HH_PARTNER,
    # hh_income = SD_HHINCOME_FEB2020,
    home_sqm = SD_HOME_SQM,
    home_owner = SD_HOMEOWNER,
    # work_h = SD_WORKHOURS_FEB2020,
    health = all_of(health),
    life_sat = all_of(life_sat),
    aff_neg_1 = all_of(aff_neg_1),
    aff_neg_2 = all_of(aff_neg_2),
    aff_neg_3 = all_of(aff_neg_3),
    aff_neg_4 = all_of(aff_neg_4),
    aff_neg_5 = all_of(aff_neg_5),
    aff_neg_6 = all_of(aff_neg_6),
    aff_pos_1 = all_of(aff_pos_1),
    aff_pos_2 = all_of(aff_pos_2),
    aff_pos_3 = all_of(aff_pos_3),
    act_wrk = all_of(act_wrk),
    act_spo = all_of(act_spo),
    act_frn = all_of(act_frn),
    act_sho = all_of(act_sho),
    act_pet = all_of(act_pet),
    sat_dem = all_of(sat_dem),
    sat_dem = all_of(sat_dem),
    work_h = all_of(work_h),
    work_homeoff = all_of(work_homeoff),
    hh_income = all_of(hh_income),
    med_txt_kro = all_of(med_txt_kro),
    med_txt_sta = all_of(med_txt_sta),
    med_txt_pre = all_of(med_txt_pre),
    med_txt_oes = all_of(med_txt_oes),
    med_txt_kur = all_of(med_txt_kur),
    med_txt_slz = all_of(med_txt_slz),
    med_txt_son = all_of(med_txt_son),
    med_vid_orf = all_of(med_vid_orf),
    med_vid_pri = all_of(med_vid_pri),
    soc_med_fb = all_of(soc_med_fb),
    soc_med_tw = all_of(soc_med_tw),
    soc_med_ig = all_of(soc_med_ig),
    soc_med_yt = all_of(soc_med_yt),
    soc_med_wa = all_of(soc_med_wa),
    soc_med_like_share = all_of(soc_med_like_share),
    soc_med_read = all_of(soc_med_read),
    soc_med_post = all_of(soc_med_post),
    risk_prop = all_of(risk_prop),
    loc_cntrl_int_1 = all_of(loc_cntrl_int_1),
    loc_cntrl_int_2 = all_of(loc_cntrl_int_2),
    loc_cntrl_int_3 = all_of(loc_cntrl_int_3),
    loc_cntrl_int_4 = all_of(loc_cntrl_int_4),
    trst_media = all_of(trst_media),
    trst_police = all_of(trst_police),
    trst_media = all_of(trst_media),
    trst_hlthsec = all_of(trst_hlthsec),
    trst_gov = all_of(trst_gov),
    trst_army = all_of(trst_army),
    corona_pos = all_of(corona_pos)
  )
```

Make new documentation with selected variables.

```{r}
doc_selected <- filter(doc, Variable %in% c(
  "RESPID",
  "SD_GENDER",
  "SD_ACCESS_BALCONY",
  "SD_ACCESS_GARDEN",
  "SD_BIRTHYEAR",
  "SD_BORN_AUSTRIA",
  "SD_MIGR_BACKGR",
  "SD_BULA",
  "SD_EDU",
  "SD_EMPLSTATUS_FEB2020",
  "SD_HH_ADULTS",
  "SD_HH_CHILD18",
  "SD_HH_TEENS",
  "SD_HH_CHILD14",
  "SD_HH_CHILD5",
  "SD_HH_CHILD2",
  "SD_HH_OLDERFAM",
  "SD_HH_OUTERFAM",
  "SD_HH_PARTNER",
  "SD_HHINCOME_FEB2020",
  "SD_HOME_SQM",
  "SD_HOMEOWNER",
  "SD_WORKHOURS_FEB2020",
  health[1],
  life_sat[1],
  aff_neg_1[1],
  aff_neg_2[1],
  aff_neg_3[1],
  aff_neg_4[1],
  aff_neg_5[1],
  aff_neg_6[1],
  aff_pos_1[1],
  aff_pos_2[1],
  aff_pos_3[1],
  act_wrk[1],
  act_spo[1],
  act_frn[1],
  act_sho[1],
  act_pet[1],
  sat_dem[1],
  work_h[1],
  work_homeoff[1],
  hh_income[1],
  med_txt_kro[1],
  med_txt_sta[1],
  med_txt_pre[1],
  med_txt_oes[1],
  med_txt_kur[1],
  med_txt_slz[1],
  med_txt_son[1],
  med_vid_orf[1],
  med_vid_pri[1],
  soc_med_fb[1],
  soc_med_tw[1],
  soc_med_ig[1],
  soc_med_yt[1],
  soc_med_wa[1],
  soc_med_like_share[1],
  soc_med_post[1],
  soc_med_read[1],
  risk_prop[1],
  loc_cntrl_int_1[1],
  loc_cntrl_int_2[1],
  loc_cntrl_int_3[1],
  loc_cntrl_int_4[1],
  trst_media[1],
  trst_police[1],
  trst_media[1],
  trst_hlthsec[1],
  trst_gov[1],
  trst_army[1],
  corona_pos[1]
  ))
write.csv(doc_selected, "data/variables_selected.csv")
```

## Recode variables

```{r}
d_wide %<>%
  mutate_at(vars(everything(.)), funs(na_if(., 88))) %>%
  mutate_at(vars(everything(.)), funs(na_if(., 99))) %>%
  mutate(
    male = 2 - .$gender,
    age = 2021 - .$year_birth,
    res_vienna = recode(.$county, `8` = 1L, .default = 0L,),
    born_aus = 2 - .$born_aus,
    home_owner = 2 - .$home_owner,
    employment_fac = factor(.$employment, 
                           labels = c("Unemployed",
                                      "Industrie",
                                      "Public service",
                                      "Self-employed",
                                      "Retired",
                                      "Housekeeping",
                                      "Student",
                                      "Incapacitated",
                                      "Parental Leave"),
                            levels = c(4, 1:3, 5:8, 10) # make unemployment reference cat
                           ),
    edu_fac = factor(.$edu,
                     labels = c("No degree", 
                                "Middle school",
                                "Vocational school",
                                "Technical school",
                                "High school",
                                "Applied high school",
                                "State college",
                                "Bachelor",
                                "Master",
                                "PhD")
                     ))
```

## Make long data format

```{r cache=T}
d_long <-
  d_wide %>% 
  pivot_longer(
    cols = health...W1:corona_pos...W32,
    names_to = "item",
    values_to = "value"
  ) %>% 
  separate(item, c("item", "wave"), sep = "\\.\\.\\.", extra = "merge") %>% 
  pivot_wider(names_from = "item", values_from = "value")
```

## Recode values

```{r}
# recode such that higher values imply more strength / align with wording
d_long %<>% 
  mutate_at(vars(med_txt_kro:med_vid_pri, health, sat_dem, soc_med_fb:soc_med_post), 
            funs(recode(., `1` = 5L, `2` = 4L, `3` = 3L, `4` = 2L, `5` = 1L))) %>% 
  mutate_at(vars(loc_cntrl_int_1:loc_cntrl_int_4), 
            funs(recode(., `1` = 4L, `2` = 3L, `3` = 2L, `4` = 1L))) %>% 
  mutate_at(vars(born_aus_prnts), 
            funs(recode(., `3` = 0L, `2` = 2L, `1` = 1L)))

# recode inverted items
d_long %<>%
  mutate_at(vars(loc_cntrl_int_3, loc_cntrl_int_4), 
            funs(recode(., `1` = 4L, `2` = 3L, `3` = 2L, `4` = 1L)))

# recode other
d_long %<>%
  mutate(
    wave = gsub("W", "", .$wave) %>% as.integer(),
    id = as.integer(id)
  )
```

## Order dataset

```{r}
d_long %<>%
  arrange(id, wave)

# create backup bc comp takes long
d_long_backup <- d_long
```

## Impute data

Next we impute data. Note that the actual imputation below is deactivated and loaded from memory to save time.

### Prep

Determine amount of missingness per respondent per wave. Because calculation takes long, this chunk is loaded from memory.

```{r}
vars_used <- c("life_sat", "aff_pos_1", "aff_pos_2", "aff_pos_3", "aff_neg_1", "aff_neg_2", "aff_neg_3", "aff_neg_4", "aff_neg_5", "aff_neg_6", "soc_med_read", "soc_med_like_share", "soc_med_post", "soc_med_fb", "soc_med_ig", "soc_med_wa", "soc_med_yt", "soc_med_tw", "age", "male", "born_aus", "born_aus_prnts", "edu_fac", "employment_fac", "health", "res_vienna", "acc_bal", "acc_gar", "home_sqm", "med_txt_kro", "med_txt_sta", "med_txt_pre", "med_txt_oes", "med_txt_kur", "med_txt_slz", "med_txt_son", "med_vid_orf", "med_vid_pri", "risk_prop", "loc_cntrl_int_1", "loc_cntrl_int_2", "loc_cntrl_int_3", "loc_cntrl_int_4", "act_wrk", "act_spo", "act_frn", "act_sho", "act_pet", "sat_dem", "trst_media", "trst_police", "trst_media", "trst_hlthsec", "trst_gov", "trst_army", "corona_pos") # only include vars measured at _all_ points
```

Filter respondents with more than 50% missing data -- only needed for analyses as originally preregistered (see additional analyses).

```{r eval=T}
d_long_50 <- 
  d_long %>% 
  mutate(na_perc = rowSums(is.na(select(., all_of(vars_used))) / ncol(select(., all_of(vars_used))))) %>% 
  filter(na_perc < .5)
write_csv(d_long_50, "data/data_50.csv")
```

Exclude social media use data, because they were measured only on selected waves.

```{r}
vars_excl <- c("soc_med_read", "soc_med_like_share", "soc_med_post", "soc_med_fb", "soc_med_ig", "soc_med_wa", "soc_med_yt", "soc_med_tw")
incl_ma <- d_long %>% 
  mutate(across(.cols = everything(), .fns = is.na))
incl_ma[vars_excl] <- FALSE

# now also for data where 50% missing excluded
incl_ma_50 <- d_long_50 %>% 
  mutate(across(.cols = everything(), .fns = is.na))
incl_ma_50[vars_excl] <- FALSE
```

### Single imputation

For analyses as originally preregistered (see additional analyses), hence only participants who provided more than 50% of all data.

```{r imputation-single-50, eval=F, cache=T}
d_long_50_imp <- mice(d_long_50, 
                   method = "pmm", # use predictive mean matching
                   m = 1, maxit = 30, # only 1 imputation
                   where = incl_ma_50,
                   seed = 180719, print = FALSE)
d_long_50_imp <- mice::complete(d_long_50_imp)
write_csv(d_long_50_imp, "data/data_50_imputed.csv")
```

Because CFAs aren't evaluated with multiple imputation, impute single data-set. Missing data was imputed for everyone.

```{r imputation-single-100, eval=F, cache=T}
d_long_100_imp <- mice(d_long, 
                   method = "pmm", # use predictive mean matching
                   m = 1, maxit = 30, # only 1 imputation
                   where = incl_ma,
                   seed = 180719, print = FALSE)
d_long_100_imp <- mice::complete(d_long_100_imp)
write_csv(d_long_100_imp, "data/data_100_imputed.csv")
```

### Multiple Imputation

Now, multiple imputation of data-sets (5 data sets, 5 iterations), used for the final analyses.

```{r imputation-mult, eval=F, cache=T}
# impute missing data with multiple imputation
d_long_mim_mice <- mice(d_long, 
                   method = "pmm", # use predictive mean matching
                   m = 5, maxit = 5, # 5 imputations, 5 iterations
                   where = incl_ma,
                   seed = 180719, print = FALSE)
d_long_mim <- mice::complete(d_long_mim_mice, action = "long", include = TRUE)
write_csv(d_long_mim, "data/data_100_mim.csv")
```

```{r eval=T}
# to further increase speed, you can also load the imputed data from the directory
# d_long_imp <- read_csv("data/data_imputed.csv")
# d_long_mim <- read_csv("data/data_imputed_mim.csv")
# d_long_imp <- read_csv("data/data_imputed_50.csv")  # data where people with >50% missing data were filtered
# d_long_mim <- read_csv("data/data_imputed_mim_50.csv")  # data where people with >50% missing data were filtered
d_long_50_imp <- read_csv("data/data_50_imputed.csv") # data where all people were included
d_long_100_imp <- read_csv("data/data_100_imputed.csv") # data where all people were included
d_long_100_mim <- read_csv("data/data_100_mim.csv") # data where all people were included
```

## Create within-between data

First, create means for scales. Then, create mean values for each person (between), and unique changes per wave (within).

```{r}
d_long_mim <-
  d_long_100_mim %>% 
  mutate(aff_pos_m = rowMeans(select(., aff_pos_1 : aff_pos_3)),
         aff_neg_m = rowMeans(select(., aff_neg_1 : aff_neg_6)),
         loc_cntrl_int_m = rowMeans(select(., loc_cntrl_int_1 : loc_cntrl_int_4)))

d_long_mim %<>%
  group_by(id) %>% 
  mutate_at(vars(health:corona_pos, loc_cntrl_int_m), funs(b = mean(., na.rm = TRUE), w = . - mean(., na.rm = TRUE))) %>% 
  ungroup()

d_long_mim_mice <- as.mids(d_long_mim)
```

```{r}
d_long_100_imp <-
  d_long_100_imp %>% 
  mutate(aff_pos_m = rowMeans(select(., aff_pos_1 : aff_pos_3)),
         aff_neg_m = rowMeans(select(., aff_neg_1 : aff_neg_6)),
         loc_cntrl_int_m = rowMeans(select(., loc_cntrl_int_1 : loc_cntrl_int_4)))

d_long_100_imp %<>%
  group_by(id) %>% 
  mutate_at(vars(health:corona_pos, loc_cntrl_int_m), funs(b = mean(., na.rm = TRUE), w = . - mean(., na.rm = TRUE))) %>% 
  ungroup()
```

And because later we want to rerun the results as originally preregistered, we'll now do the same for analyses without filtered data.

```{r}
d_long_50_imp <-
  d_long_50_imp %>% 
  mutate(aff_pos_m = rowMeans(select(., aff_pos_1 : aff_pos_3)),
         aff_neg_m = rowMeans(select(., aff_neg_1 : aff_neg_6)),
         loc_cntrl_int_m = rowMeans(select(., loc_cntrl_int_1 : loc_cntrl_int_4)))

d_long_50_imp %<>% 
  group_by(id) %>% 
  mutate_at(vars(health:corona_pos, loc_cntrl_int_m), 
            funs(b = mean(., na.rm = TRUE), w = . - mean(., na.rm = TRUE))) %>% 
  ungroup()
```

And because later we want to rerun the results without imputed data, now the same for data without imputation.

```{r}
d_long_50 %<>% 
  mutate(aff_pos_m = rowMeans(select(., aff_pos_1 : aff_pos_3)),
         aff_neg_m = rowMeans(select(., aff_neg_1 : aff_neg_6)),
         loc_cntrl_int_m = rowMeans(select(., loc_cntrl_int_1 : loc_cntrl_int_4)))

d_long_50 %<>% 
  group_by(id) %>% 
  mutate_at(vars(health:corona_pos, loc_cntrl_int_m), funs(b = mean(., na.rm = TRUE), w = . - mean(., na.rm = TRUE))) %>% 
  ungroup()
```

And now the same for the standardized data set.

```{r}
# first standardize
d_long_mim_std <-
  d_long_100_mim %>% 
  group_by(.imp) %>% 
  mutate_at(vars(gender:corona_pos, -id, -wave, -gender, -male, -born_aus, -born_aus_prnts, -edu_fac, -employment_fac, -res_vienna, -acc_bal, -acc_gar), ~ c(scale(.))) %>% 
  ungroup()

d_long_mim_std %<>%
  mutate(aff_pos_m = rowMeans(select(., aff_pos_1 : aff_pos_3)),
         aff_neg_m = rowMeans(select(., aff_neg_1 : aff_neg_6)),
         loc_cntrl_int_m = rowMeans(select(., loc_cntrl_int_1 : loc_cntrl_int_4)))

d_long_mim_std %<>%
  group_by(id) %>%
  mutate_at(vars(health:corona_pos, loc_cntrl_int_m), funs(b = mean(., na.rm = TRUE), w = . - mean(., na.rm = TRUE))) %>%
  ungroup()

d_long_mim_mice_std <- as.mids(d_long_mim_std)
```

# Measures
## Well-being
### Life satisfaction

```{r}
model_life_sat <- lmer(life_sat ~ (1 | id) + (1 | wave), d_long_100_imp)
summary(model_life_sat)
```

### Positive affect

Positive affect was measured as a scale. We hence first inspect factorial validity using CFA. 

We first test assumption of multivariate normality.

```{r eval=F}
mardia(d_long_100_imp %>% select(aff_pos_1, aff_pos_2, aff_pos_3))
```

Assumption of multivariate normal distribution was violated; hence, robust estimator will be used.


```{r}
model <- "
aff_pos =~ a1*aff_pos_1 + a2*aff_pos_2 + a3*aff_pos_3
"
cfa_aff_pos <- cfa(model, d_long_100_imp, group = "wave", estimator = "MLM")
cfa_aff_pos_50 <- cfa(model, d_long_50_imp, group = "wave", estimator = "MLM")
summary(cfa_aff_pos, standardized = TRUE, fit = TRUE, estimates = FALSE)
```

The data fit the model very well, `r td::fit_txt(cfa_aff_pos)`.
Let's next inspect reliability.

```{r}
rel_aff_pos <- get_rel(cfa_aff_pos)
```

The average reliability across all waves was omega = `r rel_aff_pos[[1]]`, hence good.

Let's next expect the development across waves.

```{r}
model_aff_pos <- lmer(aff_pos_m ~ (1 | id) + (1 | wave), d_long_100_imp)
summary(model_aff_pos)
```

Let's now export factor scores.

```{r}
d_long_50_imp$aff_pos_fs <- get_fs(cfa_aff_pos_50)
```

### Negative affect

Negative affect was measured as a scale. We hence inspect factorial validity using CFA.

We first test assumption of multivariate normality. (Warning, as these analyses take long and require much working memory, they're deactivated currently.)

```{r eval=FALSE}
mardia(d_long_100_imp %>% select(aff_neg_1, aff_neg_2, aff_neg_3, aff_neg_4, aff_neg_5, aff_neg_6))
```

Assumption of multivariate normal distribution was violated; hence, robust estimator will be used.

```{r}
model <- "
aff_neg =~ a1*aff_neg_1 + a2*aff_neg_2 + a3*aff_neg_3 + a4*aff_neg_4 + a5*aff_neg_5 + a6*aff_neg_6
"
cfa_aff_neg <- cfa(model, d_long_100_imp, group = "wave", estimator = "MLM")
cfa_aff_neg_50 <- cfa(model, d_long_50_imp, group = "wave", estimator = "MLM")
summary(cfa_aff_neg, standardized = TRUE, fit = TRUE, estimates = FALSE)
```

The data fit the model very well, `r td::fit_txt(cfa_aff_neg)`.

Let's next inspect reliability.

```{r}
rel_aff_neg <- get_rel(cfa_aff_neg)
```

The average reliability across all waves was omega = `r rel_aff_neg[[1]]`, hence good.

```{r}
model_aff_neg <- lmer(aff_neg_m ~ (1 | id) + (1 | wave), d_long_100_imp)
summary(model_aff_neg)
```

Let's now export factor scores.

```{r}
d_long_50_imp$aff_neg_fs <- get_fs(cfa_aff_neg_50)
```

## Social media use

Social media use (and channels) were measured at waves 1, 2, 8, 17, 23, 28, and for everyone who was newly recruited during the study at the first wave.

### Reading

```{r}
model_soc_med_read <- lmer(soc_med_read ~ (1 | id) + (1 | wave), d_long_100_imp)
summary(model_soc_med_read)
```

### Liking & sharing

```{r}
model_soc_med_like_share <- lmer(soc_med_like_share ~ (1 | id) + (1 | wave), d_long_100_imp)
summary(model_soc_med_like_share)
```

### Posting

```{r}
model_soc_med_post <- lmer(soc_med_post ~ (1 | id) + (1 | wave), d_long_100_imp)
summary(model_soc_med_post)
```

## Social media channels
### Facebook

```{r}
model_soc_med_fb <- lmer(soc_med_fb ~ (1 | id) + (1 | wave), d_long_100_imp)
summary(model_soc_med_fb)
```

### Twitter

```{r}
model_soc_med_tw <- lmer(soc_med_tw ~ (1 | id) + (1 | wave), d_long_100_imp)
summary(model_soc_med_tw)
```

Interestingly, lme4 throws a warning, likely because there is too little variance across waves, while little variation measure itself. Let's inspect the raw means.

```{r}
soc_med_tw_m <- d_long_100_imp %>% group_by(wave) %>% summarise(value = mean(soc_med_tw, na.rm = T))
soc_med_tw_m
```

Inspecting the means shows that the data are intact, only that the estimation didn't fully work.

### Instagram

```{r}
model_soc_med_ig <- lmer(soc_med_ig ~ (1 | id) + (1 | wave), d_long_100_imp)
summary(model_soc_med_ig)
```

### WhatsApp

```{r}
model_soc_med_wa <- lmer(soc_med_wa ~ (1 | id) + (1 | wave), d_long_100_imp)
summary(model_soc_med_wa)
```

### YouTube

```{r}
model_soc_med_yt <- lmer(soc_med_yt ~ (1 | id) + (1 | wave), d_long_100_imp)
summary(model_soc_med_yt)
```

## Locus of control

The only other variable that was measured as a scale was Locus of Control. Below I hence report the scale's factorial validity. Waves for which not a sufficient number of respondents took part were excluded.

```{r eval=T}
model <- "
loc_cntrl_int =~ a1*loc_cntrl_int_1 + a2*loc_cntrl_int_2 + a3*loc_cntrl_int_3 + a4*loc_cntrl_int_4
# loc_cntrl_int_1 ~~ loc_cntrl_int_2
loc_cntrl_int_3 ~~ loc_cntrl_int_4
"
# cfa_loc_cntrl_int <- cfa(model, filter(d_long_imp, wave != 20), group = "wave")
cfa_loc_cntrl_int <- cfa(model, filter(d_long_100_imp, wave != 20,  wave != 26, wave != 27, wave != 29, wave != 31, wave != 32), group = "wave")
summary(cfa_loc_cntrl_int, standardized = TRUE, fit = TRUE, estimates = FALSE)
```

The data fit the model very well, `r td::fit_txt(cfa_loc_cntrl_int)`.

The model didn't converge, likely for reasons of complexity, which is why the fit indices cannot be reported here.

## Figure

Display the results in a combined figure.

```{r}
fig_desc_dat <- data.frame(
  rbind(
    data.frame(type = "Life satisfaction", dimension = "Life satisfaction", get_dat(model_life_sat)),
    data.frame(type = "Affect", dimension = "Positive", get_dat(model_aff_pos)),
    data.frame(type = "Affect", dimension = "Negative", get_dat(model_aff_neg)),
    data.frame(type = "Social media use", dimension = "Reading", get_dat(model_soc_med_read)),
    data.frame(type = "Social media use", dimension = "Liking & Sharing", get_dat(model_soc_med_like_share)),
    data.frame(type = "Social media use", dimension = "Posting", get_dat(model_soc_med_post)),
    data.frame(type = "Social media channel", dimension = "Facebook", get_dat(model_soc_med_fb)),
    data.frame(type = "Social media channel", dimension = "Twitter", get_dat(model_soc_med_tw)),
    data.frame(type = "Social media channel", dimension = "Instagram", get_dat(model_soc_med_ig)),
    data.frame(type = "Social media channel", dimension = "WhatsApp", get_dat(model_soc_med_wa)),
    data.frame(type = "Social media channel", dimension = "YouTube", get_dat(model_soc_med_yt))
  ) %>% 
    mutate(
      type = factor(.$type, levels = c("Life satisfaction", "Affect", "Social media use", "Social media channel")),
      dimension = factor(.$dimension, levels = c("Life satisfaction", "Positive", "Negative", "Reading", "Liking & Sharing", "Posting", "Facebook", "Twitter", "Instagram", "WhatsApp", "YouTube"))
      )
)

fig_desc_life_sat <- make_graph(
  fig_desc_dat %>% filter(type == "Life satisfaction"), 
  title = "Life satisfaction", 
  ll = 0, ul = 10, 
  lmer = FALSE, 
  line = TRUE,
  legend = FALSE
  )

fig_desc_aff <- make_graph(
  fig_desc_dat %>% filter(type == "Affect"), 
  title = "Affect", 
  ll = 1, ul = 5, 
  lmer = FALSE, 
  line = TRUE
  )

fig_desc_soc_med_use <- make_graph(
  fig_desc_dat %>% filter(type == "Social media use"), 
  title = "Social media use", 
  ll = 1, ul = 5, 
  lmer = FALSE, 
  line = TRUE
  )

fig_desc_soc_med_channel <- make_graph(
  fig_desc_dat %>% filter(type == "Social media channel"), 
  title = "Social media channel", 
  ll = 1, ul = 5, 
  lmer = FALSE, 
  line = TRUE
  )

fig_desc <- grid.arrange(fig_desc_life_sat, fig_desc_aff, 
                         fig_desc_soc_med_use, fig_desc_soc_med_channel,
                         nrow = 2, ncol = 2)

ggsave("figures/fig_descriptives.png", 
       width = 10, height = 5,
       plot = fig_desc)
```

## Table

```{r}
tab_desc_dat <- rbind(
    "Life satisfaction" = get_specs(model_life_sat),
    "Positive affect" = get_specs(model_aff_pos),
    "Negative affect" = get_specs(model_aff_neg),
    "Read" = get_specs(model_soc_med_read),
    "Like & share" = get_specs(model_soc_med_like_share),
    "Posting" = get_specs(model_soc_med_post),
    "Facebook" = get_specs(model_soc_med_fb),
    "Twitter" = c(sd = get_specs(model_soc_med_tw)$sd,
                  min = min(soc_med_tw_m$value, na.rm = TRUE),
                  max = max(soc_med_tw_m$value, na.rm = TRUE),
                  mean = mean(soc_med_tw_m$value, na.rm = TRUE)
                  ),
    "Instagram" = get_specs(model_soc_med_ig),
    "WhatsApp" = get_specs(model_soc_med_wa),
    "YouTube" = get_specs(model_soc_med_yt)
    ) %>%
  as.data.frame()
tab_desc_dat
```

# Analyses

Before running the analyses, let's briefly check multicollinearity.

```{r}
d_long_100_imp %>% 
  filter(wave == 1) %>% 
  select(soc_med_read, soc_med_post, soc_med_like_share) %>% 
  cor(use = "pairwise.complete.obs")
```

Shows that communication types aren't collinear.

```{r}
d_long_100_imp %>% 
  filter(wave == 1) %>% 
  select(soc_med_fb, soc_med_ig, soc_med_tw, soc_med_wa, soc_med_yt) %>% 
  cor(use = "pairwise.complete.obs")
```

Shows that communication channels aren't collinear.

## Publication
### Life satisfaction

```{r}
model_life_sat_lmer_pub <- with(d_long_mim_mice, exp =  
                                lmerTest::lmer(life_sat ~
                                        (1 | id) + (1 | wave) + 
                                        soc_med_read_w + soc_med_like_share_w + soc_med_post_w  + 
                                        soc_med_fb_w + soc_med_ig_w + soc_med_wa_w + soc_med_yt_w + soc_med_tw_w +
                                        soc_med_read_b + soc_med_like_share_b + soc_med_post_b + 
                                        soc_med_fb_b + soc_med_ig_b + soc_med_wa_b + soc_med_yt_b + soc_med_tw_b +  
                                        age + male + born_aus + born_aus_prnts + edu_fac + employment_fac +
                                        res_vienna + acc_bal + acc_gar + home_sqm + corona_pos +
                                        hh_income_b +
                                        hh_adults +
                                        hh_child18 + hh_child17 + hh_child14 + hh_child5 + hh_child2 + hh_oldfam + hh_outfam + hh_partner +
                                        home_owner +
                                        med_txt_kro_b + med_txt_sta_b + med_txt_pre_b + med_txt_oes_b + med_txt_kur_b + med_txt_slz_b + med_txt_son_b + 
                                        med_vid_orf_b + med_vid_pri_b + 
                                        risk_prop_b + loc_cntrl_int_m_b + 
                                        act_wrk_w + act_spo_w + act_frn_w + act_sho_w + act_pet_w + 
                                        act_wrk_b + act_spo_b + act_frn_b + act_sho_b + act_pet_b +
                                        sat_dem_w + sat_dem_b + 
                                        health_w + health_b
                                      ))
model_life_sat_lmer_pub <- summary(pool(model_life_sat_lmer_pub), conf.int = TRUE)
model_life_sat_lmer_pub %>% 
  as.data.frame %>% 
  select(term, estimate, `2.5 %`, `97.5 %`, p.value) %>% 
  mutate(p.value = td::my_round(p.value, "p"))
```

### Positive Affect

```{r}
model_aff_pos_lmer_pub <- with(d_long_mim_mice, exp =  
                           lmerTest::lmer(aff_pos_m ~ 
                                        (1 | id) + (1 | wave) + 
                                        soc_med_read_w + soc_med_like_share_w + soc_med_post_w  + 
                                        soc_med_fb_w + soc_med_ig_w + soc_med_wa_w + soc_med_yt_w + soc_med_tw_w +
                                        soc_med_read_b + soc_med_like_share_b + soc_med_post_b + 
                                        soc_med_fb_b + soc_med_ig_b + soc_med_wa_b + soc_med_yt_b + soc_med_tw_b +  
                                        age + male + born_aus + born_aus_prnts + edu_fac + employment_fac +
                                        res_vienna + acc_bal + acc_gar + home_sqm + corona_pos +
                                        hh_income_b +
                                        hh_adults +
                                        hh_child18 + hh_child17 + hh_child14 + hh_child5 + hh_child2 + hh_oldfam + hh_outfam + hh_partner +
                                        home_owner +
                                        med_txt_kro_b + med_txt_sta_b + med_txt_pre_b + med_txt_oes_b + med_txt_kur_b + med_txt_slz_b + med_txt_son_b + 
                                        med_vid_orf_b + med_vid_pri_b + 
                                        risk_prop_b + loc_cntrl_int_m_b + 
                                        act_wrk_w + act_spo_w + act_frn_w + act_sho_w + act_pet_w + 
                                        act_wrk_b + act_spo_b + act_frn_b + act_sho_b + act_pet_b +
                                        sat_dem_w + sat_dem_b + 
                                        health_w + health_b
                                        ))
model_aff_pos_lmer_pub <- summary(pool(model_aff_pos_lmer_pub), conf.int = TRUE)
model_aff_pos_lmer_pub %>% 
  as.data.frame %>% 
  select(term, estimate, `2.5 %`, `97.5 %`, p.value) %>% 
  mutate(p.value = td::my_round(p.value, "p"))
```

### Negative Affect

```{r}
model_aff_neg_lmer_pub <- with(d_long_mim_mice, exp =  
                               lmerTest::lmer(aff_neg_m ~ 
                                        (1 | id) + (1 | wave) + 
                                        soc_med_read_w + soc_med_like_share_w + soc_med_post_w  + 
                                        soc_med_fb_w + soc_med_ig_w + soc_med_wa_w + soc_med_yt_w + soc_med_tw_w +
                                        soc_med_read_b + soc_med_like_share_b + soc_med_post_b + 
                                        soc_med_fb_b + soc_med_ig_b + soc_med_wa_b + soc_med_yt_b + soc_med_tw_b +  
                                        age + male + born_aus + born_aus_prnts + edu_fac + employment_fac +
                                        res_vienna + acc_bal + acc_gar + home_sqm + corona_pos +
                                        hh_income_b +
                                        hh_adults +
                                        hh_child18 + hh_child17 + hh_child14 + hh_child5 + hh_child2 + hh_oldfam + hh_outfam + hh_partner +
                                        home_owner +
                                        med_txt_kro_b + med_txt_sta_b + med_txt_pre_b + med_txt_oes_b + med_txt_kur_b + med_txt_slz_b + med_txt_son_b + 
                                        med_vid_orf_b + med_vid_pri_b + 
                                        risk_prop_b + loc_cntrl_int_m_b + 
                                        act_wrk_w + act_spo_w + act_frn_w + act_sho_w + act_pet_w + 
                                        act_wrk_b + act_spo_b + act_frn_b + act_sho_b + act_pet_b +
                                        sat_dem_w + sat_dem_b + 
                                        health_w + health_b
                                        ))
model_aff_neg_lmer_pub <- summary(pool(model_aff_neg_lmer_pub), conf.int = TRUE)
model_aff_neg_lmer_pub %>% 
  as.data.frame %>% 
  select(term, estimate, `2.5 %`, `97.5 %`, p.value) %>% 
  mutate(p.value = td::my_round(p.value, "p"))
```

## Without control variables
### Life satisfaction

```{r}
model_life_sat_lmer_nco <- with(d_long_mim_mice, exp =  
                                lmerTest::lmer(life_sat ~
                                        (1 | id) + (1 | wave) + 
                                        soc_med_read_w + soc_med_like_share_w + soc_med_post_w  + 
                                        soc_med_fb_w + soc_med_ig_w + soc_med_wa_w + soc_med_yt_w + soc_med_tw_w +
                                        soc_med_read_b + soc_med_like_share_b + soc_med_post_b + 
                                        soc_med_fb_b + soc_med_ig_b + soc_med_wa_b + soc_med_yt_b + soc_med_tw_b
                                      ))
model_life_sat_lmer_nco <- summary(pool(model_life_sat_lmer_nco), conf.int = TRUE)
model_life_sat_lmer_nco %>% 
  as.data.frame %>% 
  select(term, estimate, `2.5 %`, `97.5 %`, p.value) %>% 
  mutate(p.value = td::my_round(p.value, "p"))
```

### Positive Affect

```{r}
model_aff_pos_lmer_nco <- with(d_long_mim_mice, exp =  
                           lmerTest::lmer(aff_pos_m ~ 
                                        (1 | id) + (1 | wave) + 
                                        soc_med_read_w + soc_med_like_share_w + soc_med_post_w  + 
                                        soc_med_fb_w + soc_med_ig_w + soc_med_wa_w + soc_med_yt_w + soc_med_tw_w +
                                        soc_med_read_b + soc_med_like_share_b + soc_med_post_b + 
                                        soc_med_fb_b + soc_med_ig_b + soc_med_wa_b + soc_med_yt_b + soc_med_tw_b
                                        ))
model_aff_pos_lmer_nco <- summary(pool(model_aff_pos_lmer_nco), conf.int = TRUE)
model_aff_pos_lmer_nco %>% 
  as.data.frame %>% 
  select(term, estimate, `2.5 %`, `97.5 %`, p.value) %>% 
  mutate(p.value = td::my_round(p.value, "p"))
```

### Negative Affect

```{r}
model_aff_neg_lmer_nco <- with(d_long_mim_mice, exp =  
                               lmerTest::lmer(aff_neg_m ~ 
                                        (1 | id) + (1 | wave) + 
                                        soc_med_read_w + soc_med_like_share_w + soc_med_post_w  + 
                                        soc_med_fb_w + soc_med_ig_w + soc_med_wa_w + soc_med_yt_w + soc_med_tw_w +
                                        soc_med_read_b + soc_med_like_share_b + soc_med_post_b + 
                                        soc_med_fb_b + soc_med_ig_b + soc_med_wa_b + soc_med_yt_b + soc_med_tw_b
                                        ))
model_aff_neg_lmer_nco <- summary(pool(model_aff_neg_lmer_nco), conf.int = TRUE)
model_aff_neg_lmer_nco %>% 
  as.data.frame %>% 
  select(term, estimate, `2.5 %`, `97.5 %`, p.value) %>% 
  mutate(p.value = td::my_round(p.value, "p"))
```

## Standardized results

Then let's rerun the analyses.

### Life satisfaction

```{r}
model_life_sat_lmer_std <- with(d_long_mim_mice_std, exp =  
                                lmerTest::lmer(life_sat ~
                                        (1 | id) + (1 | wave) + 
                                        soc_med_read_w + soc_med_like_share_w + soc_med_post_w  + 
                                        soc_med_fb_w + soc_med_ig_w + soc_med_wa_w + soc_med_yt_w + soc_med_tw_w +
                                        soc_med_read_b + soc_med_like_share_b + soc_med_post_b + 
                                        soc_med_fb_b + soc_med_ig_b + soc_med_wa_b + soc_med_yt_b + soc_med_tw_b +  
                                        age + male + born_aus + born_aus_prnts + edu_fac + employment_fac +
                                        res_vienna + acc_bal + acc_gar + home_sqm + corona_pos +
                                        hh_income_b +
                                        hh_adults +
                                        hh_child18 + hh_child17 + hh_child14 + hh_child5 + hh_child2 + hh_oldfam + hh_outfam + hh_partner +
                                        home_owner +
                                        med_txt_kro_b + med_txt_sta_b + med_txt_pre_b + med_txt_oes_b + med_txt_kur_b + med_txt_slz_b + med_txt_son_b + 
                                        med_vid_orf_b + med_vid_pri_b + 
                                        risk_prop_b + loc_cntrl_int_m_b + 
                                        act_wrk_w + act_spo_w + act_frn_w + act_sho_w + act_pet_w + 
                                        act_wrk_b + act_spo_b + act_frn_b + act_sho_b + act_pet_b +
                                        sat_dem_w + sat_dem_b + 
                                        health_w + health_b
                                      ))
model_life_sat_lmer_std <- summary(pool(model_life_sat_lmer_std), conf.int = TRUE)
model_life_sat_lmer_std %>% 
  as.data.frame %>% 
  select(term, estimate, `2.5 %`, `97.5 %`, p.value) %>% 
  mutate(p.value = td::my_round(p.value, "p"))
```

### Positive Affect

```{r}
model_aff_pos_lmer_std <- with(d_long_mim_mice_std, exp =  
                           lmerTest::lmer(aff_pos_m ~ 
                                        (1 | id) + (1 | wave) + 
                                        soc_med_read_w + soc_med_like_share_w + soc_med_post_w  + 
                                        soc_med_fb_w + soc_med_ig_w + soc_med_wa_w + soc_med_yt_w + soc_med_tw_w +
                                        soc_med_read_b + soc_med_like_share_b + soc_med_post_b + 
                                        soc_med_fb_b + soc_med_ig_b + soc_med_wa_b + soc_med_yt_b + soc_med_tw_b +  
                                        age + male + born_aus + born_aus_prnts + edu_fac + employment_fac +
                                        res_vienna + acc_bal + acc_gar + home_sqm + corona_pos +
                                        hh_income_b +
                                        hh_adults +
                                        hh_child18 + hh_child17 + hh_child14 + hh_child5 + hh_child2 + hh_oldfam + hh_outfam + hh_partner +
                                        home_owner +
                                        med_txt_kro_b + med_txt_sta_b + med_txt_pre_b + med_txt_oes_b + med_txt_kur_b + med_txt_slz_b + med_txt_son_b + 
                                        med_vid_orf_b + med_vid_pri_b + 
                                        risk_prop_b + loc_cntrl_int_m_b + 
                                        act_wrk_w + act_spo_w + act_frn_w + act_sho_w + act_pet_w + 
                                        act_wrk_b + act_spo_b + act_frn_b + act_sho_b + act_pet_b +
                                        sat_dem_w + sat_dem_b + 
                                        health_w + health_b
                                        ))
model_aff_pos_lmer_std <- summary(pool(model_aff_pos_lmer_std), conf.int = TRUE)
model_aff_pos_lmer_std %>% 
  as.data.frame %>% 
  select(term, estimate, `2.5 %`, `97.5 %`, p.value) %>% 
  mutate(p.value = td::my_round(p.value, "p"))
```

### Negative Affect

```{r}
model_aff_neg_lmer_std <- with(d_long_mim_mice_std, exp =  
                               lmerTest::lmer(aff_neg_m ~ 
                                        (1 | id) + (1 | wave) + 
                                        soc_med_read_w + soc_med_like_share_w + soc_med_post_w  + 
                                        soc_med_fb_w + soc_med_ig_w + soc_med_wa_w + soc_med_yt_w + soc_med_tw_w +
                                        soc_med_read_b + soc_med_like_share_b + soc_med_post_b + 
                                        soc_med_fb_b + soc_med_ig_b + soc_med_wa_b + soc_med_yt_b + soc_med_tw_b +  
                                        age + male + born_aus + born_aus_prnts + edu_fac + employment_fac +
                                        res_vienna + acc_bal + acc_gar + home_sqm + corona_pos +
                                        hh_income_b +
                                        hh_adults +
                                        hh_child18 + hh_child17 + hh_child14 + hh_child5 + hh_child2 + hh_oldfam + hh_outfam + hh_partner +
                                        home_owner +
                                        med_txt_kro_b + med_txt_sta_b + med_txt_pre_b + med_txt_oes_b + med_txt_kur_b + med_txt_slz_b + med_txt_son_b + 
                                        med_vid_orf_b + med_vid_pri_b + 
                                        risk_prop_b + loc_cntrl_int_m_b + 
                                        act_wrk_w + act_spo_w + act_frn_w + act_sho_w + act_pet_w + 
                                        act_wrk_b + act_spo_b + act_frn_b + act_sho_b + act_pet_b +
                                        sat_dem_w + sat_dem_b + 
                                        health_w + health_b
                                        ))
model_aff_neg_lmer_std <- summary(pool(model_aff_neg_lmer_std), conf.int = TRUE)
model_aff_neg_lmer_std %>% 
  as.data.frame %>% 
  select(term, estimate, `2.5 %`, `97.5 %`, p.value) %>% 
  mutate(p.value = td::my_round(p.value, "p"))
```

# Figures

## Within

```{r warning=FALSE}
# get data
dat_fig_results_activity_pub <- get_dat_res(model_aff_neg_lmer_pub, model_aff_pos_lmer_pub, model_life_sat_lmer_pub, 
                                        type = "activity", analysis = "Regular")
dat_fig_results_channel_pub <- get_dat_res(model_aff_neg_lmer_pub, model_aff_pos_lmer_pub, model_life_sat_lmer_pub, 
                                        type = "channels", analysis = "Regular")
dat_fig_results_within_pub <- rbind(cbind(dat_fig_results_activity_pub, comm = "Activity"), 
                                cbind(dat_fig_results_channel_pub, comm = "Channel")) %>% 
  filter(type == "within")

dat_fig_results_activity_nco <- get_dat_res(model_aff_neg_lmer_nco, model_aff_pos_lmer_nco, model_life_sat_lmer_nco, 
                                        type = "activity", analysis = "No controls")
dat_fig_results_channel_nco <- get_dat_res(model_aff_neg_lmer_nco, model_aff_pos_lmer_nco, model_life_sat_lmer_nco, 
                                        type = "channels", analysis = "No controls")
dat_fig_results_within_nco <- rbind(cbind(dat_fig_results_activity_nco, comm = "Activity"), 
                                cbind(dat_fig_results_channel_nco, comm = "Channel")) %>% 
  filter(type == "within")

dat_fig_results_activity_std <- get_dat_res(model_aff_neg_lmer_std, model_aff_pos_lmer_std, model_life_sat_lmer_std, 
                                        type = "activity", analysis = "standardized")
dat_fig_results_channel_std <- get_dat_res(model_aff_neg_lmer_std, model_aff_pos_lmer_std, model_life_sat_lmer_std, 
                                        type = "channels", analysis = "standardized")
dat_fig_results_within_std <- rbind(cbind(dat_fig_results_activity_std, comm = "Activity"), 
                                cbind(dat_fig_results_channel_std, comm = "Channel")) %>% 
  filter(type == "within")

dat_fig_results_within <- rbind(
  dat_fig_results_within_pub, 
  dat_fig_results_within_nco,
  dat_fig_results_within_std
) %>% 
  mutate(Analysis = factor(Analysis, levels = c("Regular", "No controls", "standardized")))

# make figure
fig_results_within <- make_graph_res(
  data = filter(dat_fig_results_within, Analysis != "standardized"),
  sesoi = "est",
  facet = "comm"
  # , title = "Within-person effects of COVID-19 related social media use on well-being"
  )
fig_results_within

# safe figure
ggsave("figures/fig_results_within.png", 
       width = 7, height = 4,
       plot = fig_results_within)
```

## Between

```{r warning=FALSE}
# get data
dat_fig_results_activity_pub <- get_dat_res(model_aff_neg_lmer_pub, model_aff_pos_lmer_pub, model_life_sat_lmer_pub, 
                                        type = "activity", analysis = "Regular")
dat_fig_results_channel_pub <- get_dat_res(model_aff_neg_lmer_pub, model_aff_pos_lmer_pub, model_life_sat_lmer_pub, 
                                        type = "channels", analysis = "Regular")
dat_fig_results_between_pub <- rbind(cbind(dat_fig_results_activity_pub, comm = "Activity"), 
                                cbind(dat_fig_results_channel_pub, comm = "Channel")) %>% 
  filter(type == "between")

dat_fig_results_activity_nco <- get_dat_res(model_aff_neg_lmer_nco, model_aff_pos_lmer_nco, model_life_sat_lmer_nco, 
                                        type = "activity", analysis = "No controls")
dat_fig_results_channel_nco <- get_dat_res(model_aff_neg_lmer_nco, model_aff_pos_lmer_nco, model_life_sat_lmer_nco, 
                                        type = "channels", analysis = "No controls")
dat_fig_results_between_nco <- rbind(cbind(dat_fig_results_activity_nco, comm = "Activity"), 
                                cbind(dat_fig_results_channel_nco, comm = "Channel")) %>% 
  filter(type == "between")

dat_fig_results_activity_std <- get_dat_res(model_aff_neg_lmer_std, model_aff_pos_lmer_std, model_life_sat_lmer_std, 
                                        type = "activity", analysis = "standardized")
dat_fig_results_channel_std <- get_dat_res(model_aff_neg_lmer_std, model_aff_pos_lmer_std, model_life_sat_lmer_std, 
                                        type = "channels", analysis = "standardized")
dat_fig_results_between_std <- rbind(cbind(dat_fig_results_activity_std, comm = "Activity"), 
                                cbind(dat_fig_results_channel_std, comm = "Channel")) %>% 
  filter(type == "between")

dat_fig_results_between <- rbind(
  dat_fig_results_between_pub, 
  dat_fig_results_between_nco,
  dat_fig_results_between_std
) %>% 
  mutate(Analysis = factor(Analysis, levels = c("Regular", "No controls", "standardized")))

# make figure
fig_results_between <- make_graph_res(
  data = filter(dat_fig_results_between, Analysis != "standardized"),
  sesoi = "est"
  # , title = "Between-person relations of COVID-19 related social media use and well-being"
  )
fig_results_between

# safe figure
ggsave("figures/fig_results_between.png", 
       width = 7, height = 4,
       plot = fig_results_between)
```

## Selected control variables

Standardized, to allow for better comparison across differently scaled variables.

```{r warning=F, cache=T}
# make figure
fig_results_control_std <- make_graph_res(
  get_dat_res(model_aff_neg_lmer_std, model_aff_pos_lmer_std, model_life_sat_lmer_std, 
              type = "control", analysis = "standardized"),
  sesoi = "std",
  legend = FALSE,
  facet = "analysis"
  # , title = "Results of selected covariates"
  )
fig_results_control_std

# save figure
ggsave("figures/fig_results_control_std.png", 
       width = 7, height = 4,
       plot = fig_results_control_std)
```

# Tables

Table of within-person effects

```{r}
tab_within <- dat_fig_results_within

tab_within_std <-
  tab_within %>%  
  filter(Analysis == "standardized") %>% 
  select(std = estimate)

tab_within <-
  tab_within %>% 
  filter(Analysis == "Regular") %>% 
  cbind(tab_within_std) %>% 
  select(dv, iv, estimate, conf.low, conf.high, std, p.value) %>% 
  mutate(p.value = td::my_round(p.value, "p")) %>% 
  arrange(dv)

tab_within
```

```{r}
save.image("data/workspace_1.RData")
```
